\textls[-0]{\thetitle}

### 2023-03-23 metatheory2.tex
edit

% Deal with intuition
\noindentparagraph{The necessity of $\TyTkg{\cdot}$.} 
According to the equality rules $\ruleref{tyeq/pk/add}$, for a fixed $\lsig$, $\TyTkg{\lsig}$ is structurally similar to $\TyLkg{\lsig}$ but we are using dependent tuple $\pair{\cdot}{\cdot}$ instead of $\LkgAdd{\cdot}{\cdot}$ to package the fields of a linkage. We have computed several examples in \cref{fig:stlc-linkage-typing}, where the reader should also notice the high similarity between $\TyTkg{\lsig}$ and $\TyLkg{\lsig}$.

@@

However, the seemingly easier approach $\alpha$ is impossible because linkage $\TyLkg{\lsig^A}$ is uninhabited---say we have $\ell^A : \TyLkg{\lsig^A}$, then by projection we will have an impossible term $\goodTerm{T_A : \cU, T_B: \cU}{\ell^A.f}{\El{T_A} \to \El{T_B}}$ due to the nature of overridability of linkage. To make the inconsistency clearer, by double abstraction we will have an impossible function $g \coloneq \goodTerm{\cdot}{\nlam{T_A}{\nlam{T_B}{\ell^A.f}}}{\nTyPi{T_A}{\cU}{\nTyPi{T_B}{\cU}{\El{T_A} \to \El{T_B}}}} $, i.e. a function maps from arbitrary type to another arbitrary type . We can easily derive inconsistency by applying $\napp{\napp{g}{\top}}{\bot} : \top \to \bot$.

>>>>

% Deal with intuition
\noindentparagraph{The necessity of $\TyTkg{\cdot}$.}

As shown by the equality rule \ruleref{tyeq/pk/add},
for a given linkage signature $\lsig \coloneq \LSigAdd{\cdot}{\cdot}{\cdot}$,
the type $\TyTkg{\lsig}$ is structurally similar to the linkage type $\TyLkg{\lsig}$
except that $\TyTkg{\lsig}$ is a dependent tuple type---%
it packages the fields of $\lsig$ into a dependent tuple type.
%
We have computed several examples in
\cref{fig:stlc-linkage-typing}, where the reader should also notice the high
similarity between $\TyTkg{\lsig}$ and $\TyLkg{\lsig}$.

@@

However, the seemingly easier approach $\alpha$ is impossible because linkage
$\TyLkg{\lsig^A}$ is uninhabited---%
say we have $\ell^A : \TyLkg{\lsig^A}$, then by projection we will have an impossible term $\goodTerm{T_A : \cU, T_B: \cU}{\ell^A.f}{\El{T_A} \to \El{T_B}}$ due to the nature of overridability of linkage. To make the inconsistency clearer, by double abstraction we will have an impossible function $g \coloneq \goodTerm{\cdot}{\nlam{T_A}{\nlam{T_B}{\ell^A.f}}}{\nTyPi{T_A}{\cU}{\nTyPi{T_B}{\cU}{\El{T_A} \to \El{T_B}}}} $, i.e. a function maps from arbitrary type to another arbitrary type . We can easily derive inconsistency by applying $\napp{\napp{g}{\top}}{\bot} : \top \to \bot$.
